Walk Through the Petri-Net In TiKZ Tutorial

### 2019-12-14 mstemc/index.tex
add one post

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Drawing Graphs Using TikZ in Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Drawing Graphs Using TikZ in Emacs Org},
 pdfkeywords={},
 pdfsubject={This post collects working examples of drawing graphs using TikZ in Emacs Org},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

Draw a graph using TikZ

[[file:~/Dropbox/mstemc_hugo/static/img/tikz/example.pdf]]

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
\end{center}
\end{document}

>>>>

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
                  \usetikzlibrary{arrows,decorations.pathmorphing}
                  \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Petri-Net In TiKZ Tutorial}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
 pdfkeywords={},
 pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\newcommand*{\titleCM}{\begingroup
\begin{center}
\vspace{\baselineskip}
{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
\vspace{2\baselineskip}   \newline
{\large Eason Zhang with www.makesteamclear.com \par}
\vspace{\baselineskip}          \newline
{\large \today \par}
\vspace{\baselineskip}
\vfill
\setlength{\unitlength}{3pt}
\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
\vfill
\vspace{\baselineskip}
{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
\vspace{\baselineskip}
{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way. If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
\end{center}
\endgroup}
\begin{titlepage}
\titleCM
\end{titlepage}
\tableofcontents

Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
me work through the code line by line. During this example, more tikz libraries
are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
\texttt{tikzpicture} environment.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
\end{center}
\end{document}
